\tcr{Recovery of Primordial Density Field by Reversing the Lagrangian Space Nonlinear $E$-mode clustering}

### 2016-10-22 ms_disp1/ms_disp1.tex
i

\addtolength{\hoffset}{-0.525cm}
\addtolength{\textwidth}{1.05cm}
\title{Lagrangian Space Nonlinear $E$-mode clustering}

@@

Standard BAO reconstruction algorithms apply in Eulerian space.
They usually smooth the nonlinear density field on
linear scale ($\sim$10 Mpc$/h$) and reverse the large 
scale bulk flows by a negative Zel'dovich linear displacement
\citep{2007ApJ...664..675E,2009PhRvD..80l3501N,2009PhRvD..79f3523P}.
In the linear Lagrangian perturbation theory, the 
negative divergence of the the displacement field
$\bs\Psi(\bs q)$ respect to Lagrangian coordinates $\bs q$
gives the linear density field \citep{2010PhDT.........4J}.
Here we study the Lagrangian space clustering of dark matter
and use this information to estimate the initial density field.
Of course, the full displacement field $\bs\Psi(\bs q)$
is non-observable, as it requires the initial distributions of matter, however there are 
many techniques to estimate the displacement field from a final 
distribution of matter. For example, when a homogeneous initial matter distribution 
is assumed, there is a unique solution of curl-less displacement field to relate 
the initial and final distributions without shell-crossing. This solution can be 
solved by a metric transformation equation \citep{1995ApJS..100..269P,1998ApJS..115...19P}.
In 1-dimensional (1D) case, the exact solution 
simplifies to an ordering of matter elements by Eulerian coordinates.
Zhu {\it et al.} \cite{2016arXiv160907041Z} apply this algorithm to the result
of an 1D simulation \citep{2016JCAP...01..043M} and obtain an estimated
displacement field $\tilde\Psi(q)$, and find that this new method well recovers the linear
information and reconstructs 1D BAO peak in correlation function. 
In a bit more complicated 3D case, there are various
techniques to estimate $\tilde{\bs \Psi}(\bs q)$,
and we need to carefully consider effects of curl, shell-crossing in 3D cases.

Before these steps, we need to quantify the amount of linear information
that can be recovered from the full nonlinear displacement field $\bs\Psi(\bs q)$,
and further estimations $\tilde{\bs \Psi}(\bs q)$ can be compared with this result.
In this paper we run LSS $N$-body simulations and track the motion of
particles to obtain $\bs\Psi(\bs q)$. According to this we recover the linear density
field and compare to the primordial density field of the initial
conditions. We describe the simulation and density recovery algorithm in section
\ref{sec.method}, and we show the results in section \ref{sec.results}.
Discussion and conclusion are in section \ref{sec.discussion}.

@@

\section{Method}\label{sec.method}
We show the LSS simulation and displacement field setups in section \ref{ss.sim}.
In section \ref{ss.reco}, we recover the linear density field from the
displacement field $\bs\Psi(\bs q)$ from simulations.
Note that potential reconstruction algorithms are
based on an estimated displacement field $\tilde{\bs \Psi}(\bs q)$
instead of $\bs\Psi(\bs q)$. In the following sections we
use $\delta_R$ to label the recovered linear density field
from $\tilde{\bs \Psi}(\bs q)$.

@@

\subsection{Reconstruction}\label{ss.reco}
In the simulation, we use particle-ID (PID) to record the initial (Lagrangian) location ${\bs 
q}$ of particles, and the information is tracked until the $z=0$ and we can get the 
Lagrangian displacement vector ${\bs \Psi}\equiv{\bs x}-{\bs q}$ for every 
particle. Then these vectors are interpolated onto the initial Lagrangian 
coordinates ${\bs q}$ of particles and we get the displacement field ${\bs \Psi}
({\bs q})$.
To visualize the $\bs\Psi$ field, we draw a 3D uniform mesh over the volume,
and use the given $\bs\Psi$ field to deform the mesh according to the direction
and physical amplitude of $\bs\Psi$. In the top panel of Fig.\ref{fig.projection},
The resulting mesh illustrates a pseudo
``curvilinear coordinate'' similar to \cite{1995ApJS..100..269P},
however the mesh can be overlapped due to shell-crossing. The densest mesh grids
trace the densest structures of $\delta_N$, whereas the undeformed grid positions
are the Lagrangian coordinates in which we do the reconstruction.
The raw reconstructed density field is given by the differential motion of matter 
elements,
\begin{equation}
    \delta_R=-\nabla\cdot{\bs \Psi}({\bs q}).
\end{equation}
Because the reconstruction processes are implemented on Lagrangian coordinates,
$\delta_R$ takes the coordinates of $\bs q$ instead of $\bs x$.
We just write $\bs q$'s Fourier wave number
$k_q$ as $k$ to simplify the expression.

\begin{figure}[t] \centering
  \includegraphics[width=1.0\linewidth]{power.pdf}
  \caption{Power spectra of $\delta_L$, $\delta_N$, and the decomposition
  of $P_{LL}$ into correlated parts and noise terms according to equation
  (\ref{eq.power}).}
  \label{fig.recopower}
\end{figure}

@@

To quantify the linear information in the reconstructed density field, we decompose $\delta_L$ in Fourier space as
\begin{equation}\label{eq.decompose}
    \delta_L(k)=r'\delta_R+\delta_n,
\end{equation}
where $r'\delta_R$ is completely correlated with linear density $\delta_L$. Correlating equation (\ref{eq.decompose}) with $\delta_R$ gives
\begin{equation}
    P_{LR}=r'P_{RR}+P_{nR},
\end{equation}
where $P_{ij}\equiv\langle\delta_i\delta_j\rangle$ denotes the cross power 
spectrum. Since $\delta_n$ is uncorrelated with $\delta_R$, $P_{nR}=0$. With the 
definition of cross correlation coefficient $r(\delta_L,\delta_R)\equiv P_{LR}/\sqrt{P_{LL}P_{RR}}$ 
and bias $b^2=P_{RR}/P_{LL}$, we solve $r'=P_{LR}/P_{RR}=rb^{-1}$.
Note that these computations above and below can also be applied on $\delta_N$ for
comparison, by replacing ``$_R$'' with ``$_N$'' in the equations,
while we do not rewrite them explicitly
in the paper for simplicity. From these, we plot the cross 
correlation coefficient $r_{LN}=r(\delta_L,\delta_N)$ and
$r_{LR}=r(\delta_L,\delta_R)$ in Fig.\ref{fig.corr}. Clearly, $
\delta_R$ contains much more linear information on smaller scales.

According to equation (\ref{eq.decompose}), the auto power spectrum is decomposed as
\begin{equation}\label{eq.power}
    P_{LL}=r^2b^{-2}P_{RR}+P_{nn},
\end{equation}
and $P_{nn}=(1-r^2)P_{LL}$. Then we construct a Wiener filter to filter out the uncorrelated part in $\delta_R$:
\begin{equation}
    W(k)=\frac{r^2b^{-2}P_{RR}}{r^2b^{-2}P_{RR}+P_{nn}}=r^2.
\end{equation}
The optimal reconstructed density is given by
\begin{equation}
    \tilde\delta_R=Wb^{-1}\delta_R,
\end{equation}
and the optimal reconstructed power spectrum is given by
\begin{equation}\label{eq.opt}
    \tilde P=W^2b^{-2}P_{RR}=W^2P_{LL}+W^2b^{-2}P_{NN}.
\end{equation}
Here $W^2$ describes the damping of the linear power spectrum.

@@

To visualize the above algorithms, a projection of $\delta_R$ is plotted in
the bottom panel of Fig.\ref{fig.projection}, which looks closer to 
$\delta_L$ compared to $\delta_N$. However the smallest scales are unable
to be reconstructed.

@@

In Fig.\ref{fig.recopower}, we show the auto power spectra of
$\delta_L$ and $\delta_N$ in black dashed and blue solid curves.
Their difference shows the nonlinear evolution of LSS on 
small scales. Their cross power (not shown for clarity of the figure)
drops to a very low value on scales $k\gtrsim 0.1h/$Mpc,
indicating a loss of linear information in the
nonlinear power spectrum $P_{NN}$. This scenario directly
leads to how $\P_{LL}$ is decomposed according to equation
(\ref{eq.power}). In nonlinear case (with ``$_R$'' replaced
by ``$_N$'' equation (\ref{eq.power})), on small
scales $k\gtrsim 0.1h/$Mpc, $P_{LL}$ is dominated by
uncorrelated, nonlinear noise, shown in the green
dotted line. In reconstructed case, however, $P_{LL}$
is decomposed into orange dash-dotted correlated
part and purple dotted uncorrelated part according to
equation (\ref{eq.power}). The correlated power spectrum
is dominated on BAO scales of our interest.

To quantify the improvement of cross-correlation in the power
spectrum, we compute the 
damping factors $W^2(k)$ respectively for the optimal filtered 
nonlinear and reconstructed density fields $\tilde\delta_N$
and $\tilde\delta_R$.
We fit Gaussian BAO damping models
${\mathcal D}(k)=\exp(-k^2\Sigma^2/2)$ to these $W^2(k)$'s
and give $\Sigma=1.8$ Mpc$/h$ and $\Sigma=12$ 
Mpc$/h$ for reconstructed and nonlinear fields.
Since ${\mathcal D}(k)=W^2=r^4$, we plot
${\mathcal D}_N^{1/4}$ and ${\mathcal D}_R^{1/4}$
over $r_{LN}$ and $r_{LR}$ in Fig.\ref{fig.corr}.
The analyses are repeated with various box sizes (100, 300, 800 Mpc$/h$ per side)
and give consistent results.

To further illustrate the improvement in real space
one point function correlations,
in Fig.\ref{fig.pdfs} we use the probability distribution
as functions (PDFs) of $(\delta_L,\delta_N)$ and $(\delta_L,\delta_R)$
to show the point-point correlation between these two pairs of density
fields. Since $\delta_n$ in equation (\ref{eq.decompose}) is
uncorrelated, we use Wiener filtered fields. To keep the
consistency over $\delta_L$, $\delta_N$ and $\delta_R$, we
use the $W(k)=r^2_{LR}$ as the Wiener filter.
The grey-scaled plots in the center of both panels show the 2-variable PDFs,
whereas their projections onto each variable are just
1-variable PDFs -- $f(\delta_L)$, $f(\delta_N)$ and $f(\delta_R)$, shown
as red/blue curves on the axes of Fig.\ref{fig.pdfs}.
In the top panel, $\delta_N$ shows an approximate log-normal
distribution (blue curve) and $\delta_L$ follows an expected
Gaussian distribution. They show tiny positive correlation in the
2D PDF.
Because in Fourier space, $\delta_L$ and $\delta_N$ have
correlations on only very large, linear scales (Fig.\ref{fig.corr}),
they result in little correlation in real space -- initial density fluctuations
in Lagrangian coordinates are evolved/transformed to Eulerian coordinates.
As the reconstruction is done in Lagrangian space, it recovers
certain amount of correlation, as shown in the 2D PDF of the bottom panel
of Fig.\ref{fig.pdfs}. One can also see that $\delta_R$ follows
a much closer Gaussian distribution (blue curve of the bottom panel).
We notice that the less-dense regions of $\delta_L$ are strongly
correlated with $\delta_R$, whereas denser regions of $\delta_L$ are
reconstructed less better, and $\delta_R$ shows more dispersion.
These second uncorrelated peaks in the 2D PDF and $f(\delta_R)$
are caused by nonlinear effects. We examine the reconstruction on
higher redshifts, and confirm that these second uncorrelated peaks
damp out as we go to higher redshifts.

\section{Discussion and conclusion}\label{sec.discussion}
We extract the actual displacement field of matter elements in cosmological $N$-body
simulations, and use this displacement field to study the LSS nonlinear
clustering in Lagrangian space. The displacement information is used to reconstruct
the primordial linear perturbations. The result shows a prominent improvement from
$r_{LN}$ to $r_{LR}$ in Fig.\ref{fig.corr} -- recovering the lost linear information on
nearly an order of magnitude smaller scales.
This is achieved by implementing differential movement information
of matter elements on Lagrangian coordinates, rather than on
Eulerian coordinates. This result illustrates the feasibility
of using estimated displacement field $\tilde{\bs \Psi}(\bs q)$ to reconstruct primordial linear
density field. A straightforward example of a estimation of $\tilde{\bs \Psi}(\bs q)$
is given by \cite{1995ApJS..100..269P,1998ApJS..115...19P}.
%\tcr{More complicated reconstruction algorithms, e.g., least action
%algorithms \cite{1989ApJ...344L..53P,2000ApJ...544...21G} can give
%the exact $\delta_L$}, where
%shell-crossing effects are also considered.
In reality, one needs
to consider all aspects including vorticity, shell-crossing, bias, noise
and data complexities. The impact of these factors can be quantitatively
compared with the impact of different estimation methods, and with
the exact solution by $N$-body simulations.

The advantage of using displacement field in reconstruction is
its insensitive response from highly nonlinearities --
densest regions form because matter elements, after shell crossing,
stop experiencing the linear extrapolated of Zel'dovich approximation.
i.e. the displacement fields are dominated by early stage linear processes,
which is the Lagrangian-Eulerian coordinate transform,
while late stage shell-crossing, nonlinear and baryonic processes
only fine-tunes the final position $\bs x$. In contrast, traditional
treatments in reconstruction deals directly on density fields which sensitively
relies on nonlinear processes --  density values can vary by orders
of magnitude due to nonlinear/baryonic physics and many sources of errors.

>>>>

\addtolength{\hoffset}{-0.525cm}
\addtolength{\textwidth}{1.05cm}
\title{\tcr{Recovery of Primordial Density Field by Reversing the Lagrangian Space Nonlinear $E$-mode clustering}}

@@

\tcb{Standard BAO reconstruction algorithms apply in Eulerian space.
They usually smooth the nonlinear density field on
linear scale ($\sim$10 Mpc$/h$) and reverse the large 
scale bulk flows by a negative Zel'dovich linear displacement
\citep{2007ApJ...664..675E,2009PhRvD..80l3501N,2009PhRvD..79f3523P}.}
In the linear Lagrangian perturbation theory (LPT), the 
negative divergence of the the displacement field
$-\nabla_q\cdot\bs\Psi(\bs q)$ respect to Lagrangian coordinates $\bs q$
gives the linear density field \citep{2010PhDT.........4J},
\tcr{and in many literatures
\cite{2013MNRAS.428..141N,2014PhRvD..89h3515C,2016JCAP...03..017B}
$\nabla_q\cdot\bs\Psi(\bs q)$ is compared with various standard LPT
and corrected LPT initial conditions. Their motivation was
trying to correct or modify the LPT displacement fields
in order that the final positions of particles are brought
closer to $N$-body results. Their results show that 
all LPT methods are still unable to mimic the shell-crossing
scales given by $N$-body simulation. Because of the absence
of Lagrangian space information in observations, few density
reconstruction algorithms are developed according to the relation
between displacement and linear density. However,
there are techniques to estimate the displacement field from a final 
distribution of matter.}
For example, when a homogeneous initial matter distribution 
is assumed, there is a unique solution of curl-less displacement field to relate 
the initial and final distributions without shell-crossing. This solution can be 
solved by a metric transformation equation
\citep{1995ApJS..100..269P,1998ApJS..115...19P}.
In 1-dimensional (1D) case, the exact solution 
simplifies to an ordering of matter elements by Eulerian coordinates.
Zhu {\it et al.} \cite{2016arXiv160907041Z} apply this algorithm to the result
of an 1D simulation \citep{2016JCAP...01..043M} and obtain an estimated
displacement field $\tilde\Psi(q)$, and find
that this new method well recovers the linear
information and reconstructs 1D BAO peak in correlation function.
\tcr{In 3D and more realistic cases, one needs to
carefully consider effects of curl, shell-crossing, 
complicated baryonic physics and biased tracers (galaxies).}

\tcr{Before these steps, we need to quantify the amount of linear information
that can be recovered\footnote{To avoid ambiguity, we call
$\delta_R=-\nabla_q\cdot\bs\Psi(\bs q)$ recovered linear density field, which
requires $\bs\Psi(\bs q)$ from $N$-body simulations, while
$-\nabla_q\cdot\tilde{\bs \Psi}(\bs q)$ is called the
reconstructed density field.}
 from the full nonlinear displacement field $\bs\Psi(\bs q)$.
In $\bs\Psi(\bs q)$ from $N$-body simulations,
(1) shell-crossing effects are fully considered; (2) $E$-mode displacement
field is used for recovering the linear information (although $B$-mode is
also present); (3) the setup is clean in absence of baryons and realistic
observables. So it sets the best quality that potential reconstruction
algorithms can achieve and further reconstructions by $\tilde{\bs \Psi}(\bs q)$
can be compared with this result. Actually, in the later discussions and
our next works we will show that, compared to $\tilde{\bs \Psi}(\bs q)$,
additional information (shell-crossing) do not enhance the reconstruction
prominently. Further more, we study the scale dependent cross-correlation
between $-\nabla_q\cdot\bs\Psi(\bs q)$ and linear density field
and construct optimal Wiener filters to get the optimal filtered
recovered linear density field and recovered linear power spectrum.}

In the rest part of the paper, we describe the simulation,
density recovery algorithm and Wiener filter setups in section
\ref{sec.method}. We show results in section \ref{sec.results}.
Discussion and conclusion are in section \ref{sec.discussion}.

@@

\section{Method}\label{sec.method}
We show the LSS simulation and displacement field setups in section \ref{ss.sim}.
In section \ref{ss.reco}, we recover the linear density field from the
displacement field $\bs\Psi(\bs q)$ from simulations.
Note that potential reconstruction algorithms are
based on an estimated displacement field $\tilde{\bs \Psi}(\bs q)$
instead of $\bs\Psi(\bs q)$. In the following sections we
use $\delta_R$ to label the recovered linear density field
from $\bs\Psi(\bs q)$.

@@

\subsection{Density Recovery}\label{ss.reco}
In the simulation, we use particle-ID (PID) to record the initial (Lagrangian) location ${\bs 
q}$ of particles, and the information is tracked until the $z=0$ and we can get the 
Lagrangian displacement vector ${\bs \Psi}\equiv{\bs x}-{\bs q}$ for every 
particle. Then these vectors are interpolated onto the initial Lagrangian 
coordinates ${\bs q}$ of particles and we get the displacement field ${\bs \Psi}
({\bs q})$.
To visualize the $\bs\Psi$ field, we draw a 3D uniform mesh over the volume,
and use the given $\bs\Psi$ field to deform the mesh according to the direction
and physical amplitude of $\bs\Psi$. In the top panel of Fig.\ref{fig.projection},
The resulting mesh illustrates a pseudo
``curvilinear coordinate'' similar to \cite{1995ApJS..100..269P},
however the mesh can be overlapped due to shell-crossing. The densest mesh grids
trace the densest structures of $\delta_N$, whereas the undeformed grid positions
are the Lagrangian coordinates in which we do the density recovery.
The raw recovered density field is given by the differential motion of matter 
elements,
\begin{equation}
    \delta_R=-\nabla\cdot{\bs \Psi}({\bs q}).
\end{equation}
Because the recovery processes are implemented on Lagrangian coordinates,
$\delta_R$ takes the coordinates of $\bs q$ instead of $\bs x$.
We just write $\bs q$'s Fourier wave number
$k_q$ as $k$ to simplify the expression.

\begin{figure}[t] \centering
  \includegraphics[width=1.0\linewidth]{power.pdf}
  \caption{\tcr{Power spectra of $\delta_L$, $\delta_N$, and the decomposition
  of $P_{LL}$ into correlated parts and noise terms according to equation
  (\ref{eq.power}).}}
  \label{fig.recopower}
\end{figure}

@@

To quantify the linear information in the recovered density field, we decompose $\delta_L$ in Fourier space as
\begin{equation}\label{eq.decompose}
    \delta_L(k)=r'\delta_R+\delta_n,
\end{equation}
where $r'\delta_R$ is completely correlated with linear density $\delta_L$. Correlating equation (\ref{eq.decompose}) with $\delta_R$ gives
\begin{equation}
    P_{LR}=r'P_{RR}+P_{nR},
\end{equation}
where $P_{ij}\equiv\langle\delta_i\delta_j\rangle$ denotes the cross power 
spectrum. Since $\delta_n$ is uncorrelated with $\delta_R$, $P_{nR}=0$. With the 
definition of cross correlation coefficient $r(\delta_L,\delta_R)\equiv P_{LR}/\sqrt{P_{LL}P_{RR}}$ 
and bias $b^2=P_{RR}/P_{LL}$, we solve $r'=P_{LR}/P_{RR}=rb^{-1}$.
Note that these computations above and below can also be applied on $\delta_N$ for
comparison, by replacing ``$_R$'' with ``$_N$'' in the equations,
while we do not rewrite them explicitly
in the paper for simplicity. From these, we plot the cross 
correlation coefficient $r_{LN}=r(\delta_L,\delta_N)$ and
$r_{LR}=r(\delta_L,\delta_R)$ in Fig.\ref{fig.corr}. Clearly, $
\delta_R$ contains much more linear information on smaller scales.

According to equation (\ref{eq.decompose}), the auto power spectrum is decomposed as
\begin{equation}\label{eq.power}
    P_{LL}=r^2b^{-2}P_{RR}+P_{nn},
\end{equation}
and $P_{nn}=(1-r^2)P_{LL}$. Then we construct a Wiener filter to filter out the uncorrelated part in $\delta_R$:
\begin{equation}
    W(k)=\frac{r^2b^{-2}P_{RR}}{r^2b^{-2}P_{RR}+P_{nn}}=r^2.
\end{equation}
The optimal recovered density is given by
\begin{equation}
    \tilde\delta_R=Wb^{-1}\delta_R,
\end{equation}
and the optimal recovered power spectrum is given by
\begin{equation}\label{eq.opt}
    \tilde P=W^2b^{-2}P_{RR}=W^2P_{LL}+W^2b^{-2}P_{NN}.
\end{equation}
Here $W^2$ describes the damping of the linear power spectrum.

@@

To visualize the above algorithms, a projection of $\delta_R$ is plotted in
the bottom panel of Fig.\ref{fig.projection}, which looks closer to 
$\delta_L$ compared to $\delta_N$. However the smallest scale structures are unable
to be recovered.

@@

In Fig.\ref{fig.recopower}, we show the auto power spectra of
$\delta_L$ and $\delta_N$ in black dashed and blue solid curves.
Their difference shows the nonlinear evolution of LSS on 
small scales. Their cross power (not shown for clarity of the figure)
drops to a very low value on scales $k\gtrsim 0.1h/$Mpc,
indicating a loss of linear information in the
nonlinear power spectrum $P_{NN}$. This scenario directly
leads to how $P_{LL}$ is decomposed according to equation
(\ref{eq.power}). In nonlinear case (with ``$_R$'' replaced
by ``$_N$'' equation (\ref{eq.power})), on small
scales $k\gtrsim 0.1h/$Mpc, $P_{LL}$ is dominated by
uncorrelated, nonlinear noise, shown in the green
dotted line. In the case of $\delta_R$, however, $P_{LL}$
is decomposed into orange dash-dotted correlated
part and purple dotted uncorrelated part according to
equation (\ref{eq.power}). The correlated power spectrum
is dominated on BAO scales of our interest.

To quantify the improvement of cross-correlation in the power
spectrum, we compute the 
damping factors $W^2(k)$ respectively for the optimal filtered 
nonlinear and recovered density fields $\tilde\delta_N$
and $\tilde\delta_R$.
We fit Gaussian BAO damping models
${\mathcal D}(k)=\exp(-k^2\Sigma^2/2)$ to these $W^2(k)$'s
and give $\Sigma=1.8$ Mpc$/h$ and $\Sigma=12$ 
Mpc$/h$ for $\delta_R$ and $\delta_N$.
Since ${\mathcal D}(k)=W^2=r^4$, we plot
${\mathcal D}_N^{1/4}$ and ${\mathcal D}_R^{1/4}$
over $r_{LN}$ and $r_{LR}$ in Fig.\ref{fig.corr}.
The analyses are repeated with various box sizes (100, 300, 800 Mpc$/h$ per side)
and give consistent results.

To further illustrate the improvement in real space
one point function correlations,
in Fig.\ref{fig.pdfs} we use the probability distribution
as functions (PDFs) of $(\delta_L,\delta_N)$ and $(\delta_L,\delta_R)$
to show the point-point correlation between these two pairs of density
fields. Since $\delta_n$ in equation (\ref{eq.decompose}) is
uncorrelated, we use Wiener filtered fields. To keep the
consistency over $\delta_L$, $\delta_N$ and $\delta_R$, we
use the $W(k)=r^2_{LR}$ as the Wiener filter.
The grey-scaled plots in the center of both panels show the 2-variable PDFs,
whereas their projections onto each variable are just
1-variable PDFs -- $f(\delta_L)$, $f(\delta_N)$ and $f(\delta_R)$, shown
as red/blue curves on the axes of Fig.\ref{fig.pdfs}.
In the top panel, $\delta_N$ shows an approximate log-normal
distribution (blue curve) and $\delta_L$ follows an expected
Gaussian distribution. They show tiny positive correlation in the
2D PDF.
Because in Fourier space, $\delta_L$ and $\delta_N$ have
correlations on only very large, linear scales (Fig.\ref{fig.corr}),
they result in little correlation in real space -- initial density fluctuations
in Lagrangian coordinates are evolved/transformed to Eulerian coordinates.
As the recovery is done in Lagrangian space, it recovers
certain amount of correlation, as shown in the 2D PDF of the bottom panel
of Fig.\ref{fig.pdfs}. One can also see that $\delta_R$ follows
a much closer Gaussian distribution (blue curve of the bottom panel).
In denser regions of $\delta_L$, $\delta_R$ is saturated at
$\delta_R=3$, signifying the extreme collapsing of matter \citep{2013MNRAS.428..141N}:
$\delta_R=-\nabla\cdot\bs\Psi=\nabla\cdot\bs q=3$. Shell crossing
makes $\delta_R$ oscillate around 3. These second uncorrelated peaks
damp out as we go to higher redshifts. \tcr{more?}

\section{Discussion and conclusion}\label{sec.discussion}
We extract the actual displacement field of matter elements in cosmological $N$-body
simulations, and use this displacement field to study the LSS nonlinear
clustering in Lagrangian space. The displacement information is used to recover
the primordial linear perturbations. The result shows a prominent improvement from
$r_{LN}$ to $r_{LR}$ in Fig.\ref{fig.corr} -- recovering the lost linear information on
nearly an order of magnitude smaller scales.
This is achieved by implementing differential movement information
of matter elements on Lagrangian coordinates, rather than on
Eulerian coordinates. This result illustrates the feasibility
of using estimated displacement field $\tilde{\bs \Psi}(\bs q)$ to reconstruct primordial linear
density field. A straightforward example of a estimation of $\tilde{\bs \Psi}(\bs q)$
is given by \cite{1995ApJS..100..269P,1998ApJS..115...19P}.
%\tcr{More complicated reconstruction algorithms, e.g., least action
%algorithms \cite{1989ApJ...344L..53P,2000ApJ...544...21G} can give
%the exact $\delta_L$}, where
%shell-crossing effects are also considered.
In reality, one needs
to consider all aspects including vorticity, shell-crossing, bias, noise
and data complexities. The impact of these factors can be quantitatively
compared with the impact of different estimation methods, and with
the exact solution by $N$-body simulations.

\tcr{The advantage of using displacement field in reconstruction is
its insensitive response from highly nonlinearities --
densest regions form because matter elements, after shell crossing,
stop experiencing the linear extrapolated of Zel'dovich approximation.
i.e. the displacement fields are dominated by early stage linear processes,
which is the Lagrangian-Eulerian coordinate transform,
while late stage shell-crossing, nonlinear and baryonic processes
only fine-tunes the final position $\bs x$
\citep{2014PhRvD..89h3515C}. Compared with estimated displacement fields $\tilde{\bs \Psi}(\bs q)$
by \cite{1995ApJS..100..269P}, which do not have shell crossing,
the additional shell-crossing information in $\bs\Psi(\bs q)$
is uncorrelated with $\delta_L$. This insensitive response from
nonlinearities enables the stability of reconstruction algorithms,
which are expected to give similar results of this paper. 
In contrast, traditional
treatments in reconstruction deals directly on density fields which sensitively
relies on nonlinear processes --  density values can vary by orders
of magnitude due to nonlinear/baryonic physics and many sources of errors.}
